City traffic, IoT and Blockchain technologies

### 2020-11-03 thesis/report2.tex
Another paragraph on report 2.

    IOTA is a distributed ledger technology, but not a blockchain, that allows devices in a IOTA network to transact in micropayments and to send each other immutable data. One crucial difference between IOTA and a blockchain is the how the transactions are linked together. In blockchain-type technologies, as the name implies, a transaction references only the one behind it and is referenced only by the one which comes next. In IOTA, being a distributed ledger technology (DLT), a transaction can reference multiple transactions which were made earlier and can be referenced by multiple transactions which comes after it. This is known as direct acyclic graph (DAG). Another crucial difference between a blockchain and IOTA DLT is the consensus mechanism. In the blockchain the consensus is made through the proof of work by the miners. In IOTA there are no miners and there is no proof of work. Instead there is an entity called The Coordinator or more recently Coordicide. Their aim is to validate transactions without requiring a proof of work mechanism. The main reason for this is to give the ability of participating to many other types of devices which otherwise do not have the power of doing proof of work tasks.

>>>>

    IOTA is a distributed ledger technology, but not a blockchain, that allows devices in a IOTA network to transact in micropayments and to send each other immutable data. One crucial difference between IOTA and a blockchain is the how the transactions are linked together. In blockchain-type technologies, as the name implies, a transaction references only the one behind it and is referenced only by the one which comes next. This gives a chain of blocks, each block being related only to two other blocks. In IOTA, being a distributed ledger technology (DLT), a transaction can reference multiple transactions which were made earlier and can be referenced by multiple transactions which comes after it. This is known as direct acyclic graph (DAG). Another crucial difference between a blockchain and IOTA DLT is the consensus mechanism. In the blockchain the consensus is made through the proof of work by the miners. In IOTA there are no miners and there is no proof of work. Instead there is an entity called The Coordinator or more recently a post coordinator named Coordicide. Their aim is to validate transactions without requiring a proof of work mechanism. The main reason for this is to give the ability of participating to many other types of devices which otherwise do not have the power of doing proof of work tasks.

    Coordicide has few specific goals. Known as the scalabilty trilemma, both in Ethereum and IOTA worlds, the guarantee of current IOTA solutions offers at most two (scalability and security) out of three characteristics from this list: scalability, security, decentralization. Coordicide aim to offers all three of them. Scalability means that the rate of transcations are not limited by the Coordicide protocols. The can scale as much as needed. Security means that the entire network cannot be attached by malicious actors. They cannot influence the consensus. Decentralization means that all nodes can be part of the consensus process and that there is no central authority to oversee it.

    \cite{EnhancingIoTSecurityIOTA} is discussing a practical approach (a smart utility meter system and a smart car transaction system) towards IoT using blockchains (Ethereum and IOTA). Their first finding is the unsuitability of Ethereum blockchain: mining is computationally intensive, poorly scaling for the raising number of IoT devices, overhead traffic because of the Ethereum protocols. Their second finding, however, is the IOTA DLT readiness for IoT devices. IOTA reference implementation specifies two types of nodes: a full node and a light node. The full node runs locally (on a ordinary computer) and can be accessed via a GUI. The light node is a local interface from the device itself to the full node it belongs to. The solution they have designed has scalability out-of-the-box, due to the nature of IOTA, partition tolerance, security through small fees which would prohibit an attacker to spam the network and the lack of peer discovery.

    % Privacy aware IOTA ledger: Decentralized mixing and unlinkable IOTA transactions
